The Prevalence of E-Mail Header Injections on the World Wide Web

### 2016-05-24 System/components.tex
fixed todos in evaluation
fixed spacing and abstract

Along with the payload, the Fuzzer also injects data into the other fields of the form. This data must pass validation constraints on the individual input fields (e.g.,\ for a name field, numbers might not be allowed).  As crawling and fuzzing input fields on the web is an open problem~\cite{raghavan2000crawling}, we chose to go with a best-effort approach. To maximize the amount of vulnerabilities the system discovers, the data injected into the input fields should adhere to the constraints. The Fuzzer uses a ``Data Dictionary'' which has predefined ``keys'' and ``values'' for standard input fields such as \texttt{name}, \texttt{date}, \texttt{username}, \texttt{password}, \texttt{text}, and \texttt{submit}.
% Adam: What does it mean here for these to be generated on-the-fly? Using templates? - Fixed.
The default values for these are generated from the Data dictionary for each form, based on generally followed guidelines for such fields. For example, password fields should consist of at least one uppercase letter, one lowercase letter, and a special character.
% Adam: can you add a sentence here about crawling and fuzzing fields on the web is an open problem (and cite ``Crawling the hidden web'' - DONE.

@@

\subsubsection{Injection Verification}
\label{Comp:EMA}
The Injection Verification module checks for the presence of injected data in the received \emails. This module works on the \emails received and stored by our Postfix server, and, depending on the user account that received the \email, it performs different functions.
\paragraph{Analyzing regular \email}
\sloppy
`Regular \email' refers to the \emails received by account \colorbox{lightgray}{\lstinline{reguser(xxxx)@example.com}} that were sent due to injecting the regular, non-malicious, payload (discussed in Section~\ref{Comp:Fuzzer:nmp}). The objective of the analysis on this \email is identify if the input fields that we injected with data appear on the resulting \email, and if so, which fields appear where.

>>>>

Along with the payload, the Fuzzer also injects data into the other fields of the form. This data must pass validation constraints on the individual input fields (e.g.,\ for a name field, numbers might not be allowed).  As crawling and fuzzing input fields on the web is an open problem~\cite{raghavan2000crawling}, we chose to go with a best-effort approach. To maximize the amount of vulnerabilities the system discovers, the data injected into the input fields should adhere to the constraints. The Fuzzer uses a ``Data Dictionary'' which has predefined ``keys'' and ``values'' for standard input fields such as \texttt{name}, \texttt{date}, \texttt{username}, \texttt{password}, \texttt{text}, and \texttt{submit}.
% Adam: What does it mean here for these to be generated on-the-fly? Using templates? - Fixed.
The values for these are generated from the Data dictionary for each form, based on generally followed guidelines for such fields. For example, password fields should consist of at least one uppercase letter, one lowercase letter, and special characters.
% Adam: can you add a sentence here about crawling and fuzzing fields on the web is an open problem (and cite ``Crawling the hidden web'' - DONE.

@@

\subsubsection{Injection Verification}
\label{Comp:EMA}
The Injection Verification module checks for the presence of injected data in the received \emails. This module works on the \emails received and stored by our Postfix server, and, depending on the user account that received the \email, it performs different functions.
\paragraph{Analyzing regular e-mail}
\sloppy
`Regular \email' refers to the \emails received by account \colorbox{lightgray}{\lstinline{reguser(xxxx)@example.com}} that were sent due to injecting the regular, non-malicious, payload (discussed in Section~\ref{Comp:Fuzzer:nmp}). The objective of the analysis on this \email is identify if the input fields that we injected with data appear on the resulting \email, and if so, which fields appear where.

### 2016-05-24 abstract.tex
fixed some small things Fixed all todos till sys design
fixed spacing and abstract

	This paper presents a scalable mechanism to automatically detect \ehi vulnerabilities and uses this mechanism to quantify the prevalence of \ehi vulnerabilities on the web. Using a black-box testing approach, the system crawled \urls URLs identify web pages which contained form fields. \forms such forms were found by the system, of which \emailforms forms contained \email fields. We then test \fuzzed forms to see if they would send us an \email, and \recd forms set us an \email. Of these \malfuzzed forms were tested with \ehi payloads and, of these, we found \success vulnerable URLs across \domains domains. Then, to demonstrate that \ehi vulnerabilities are actively being exploited to create a spamming platform, we found \ipsblacklist IPs that were vulnerable on spaming blacklists. This work shows that \ehi vulnerabilities are widespread widespread and deserve future research attention.
\end{abstract}

>>>>

	This paper presents a scalable mechanism to automatically detect \ehi vulnerabilities and uses this mechanism to quantify the prevalence of \ehi vulnerabilities on the web. Using a black-box testing approach, the system crawled \urls URLs identify web pages which contained form fields. \forms such forms were found by the system, of which \emailforms forms contained \email fields. We then tested \fuzzed forms to see if they would send us an \email, and \recd forms sent us an \email. Of these \malfuzzed forms were tested with \ehi payloads and, of these, we found \success vulnerable URLs across \domains domains. Then, to demonstrate that \ehi vulnerabilities are actively being exploited to create a spamming platform, we found \ipsblacklist IPs that were vulnerable on well-known spamming blacklists. This work shows that \ehi vulnerabilities are widespread and deserve future research attention.
\end{abstract}
